Analysing Constraint Grammars with a SAT-solver

### 2016-03-08 paper/lrec/eval_futurework.tex
update finnish running time

\clock{} all 
       rules & Xh Ymin     & Xh Ymin   & Xh Ymin &  Xh Ymin \\ \hline

@@

Both of these are internal conflicts, which may not be trivial to see.
The first rule requires the target to be genitive and unambiguously nominative; however, these two tags cannot combine in the same reading.
As for the second rule, the definition of \texttt{PP} includes \texttt{adv} among others---with the sets expanded, this rule becomes \texttt{SELECT adv IF (NOT 0 pp|adv|adp|po|pr) ...}.

@@

The first two rules together remove the target of the third, leaving no way for there to be adjective or noun.

>>>>

\clock{} all 
       rules & 2h 2min     & Xh Ymin   & Xh Ymin &  Xh Ymin \\ \hline

@@

Both of these are internal conflicts, which may not be trivial to see.
The first rule requires the target to be genitive and unambiguously nominative; however, these two tags cannot combine in the same reading.
As for the second rule, the definition of \texttt{PP} includes \texttt{adv} among others---with the sets expanded, this rule becomes \texttt{SELECT adv IF (NOT 0 pp|adv|adp|po|pr) (...)}.

@@

This is the same pattern we have already seen before, but with a set of rules as the reason for conflict.
The first two rules together remove the target of the third, leaving no way for there to be adjective or noun.
